---
title: "Assessing the Economic and Population Health Impact of Severe Weather Events using U.S. NOAA 1950-2011 Data"
author: "slgr"
date: "5 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

##Synopsis 
Storms and other severe weather events can cause both public health and economic problems for communities and municipalities. This project involves exploring the U.S. National Oceanic and Atmospheric Administration's (NOAA) storm database that tracks characteristics of major storms and weather events in the United States, including when and where they occur, as well as estimates of any fatalities, injuries, and property damage. National Weather Service Storm Data Documentation can be found 
[here](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf) and
[here](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf) and 
the source data for the analysis can be found
[here](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2).

The data analysis addresses the following two questions:

* Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

* Across the United States, which types of events have the greatest economic consequences?

##Data Processing
Load the readr package, download and read the data:
```{r}
library(readr)
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", "StormData.csv.bz2")
read_csv("StormData.csv.bz2")
```
##Results
```{r}
#results
```
